---
title: "LDA"
output: html_notebook
---


We will compare some classifiers on the "Toxic" column.

Load libraries

```{r}
library(tidyverse)
library(tictoc)
library(caret)
library(MASS)
source("./parameters.R")
```


# Open the Bag of Word with labels

```{r}
# Open the bag of words
fileName = "bow_tfidf__min_words_100_2grams_1000__sampling_balanced__cor_cut_0.5_from_1408_to_1247_rm0.csv"
df = read_csv(fileName, col_types=col_types_df)
df = df[,-c(2,3,5:9)]
# During tests, we can work on a sample
sampled = FALSE
if (sampled == TRUE) {
  set.seed(42)
  max = nrow(df)
  sampled = round(max/10)
  df = df[sample(max, sampled), ]
}
# show the data set
df
```


# Splitting the data

```{r}
# Split between train and test
df_train = df[df[1] == 1,-1]
df_test  = df[df[1] == 2,-1]

# Split the test set between features and labels
X_train = df_train[,-1]
Y_train = as.factor(df_train$df_toxic)

# Split the train set between features and labels
X_test = df_test[,-1]
Y_test = as.factor(df_test$df_toxic)
```

# Have a look

```{r}
X_train
as.data.frame(Y_train) 
X_test
as.data.frame(Y_test)
```


# Train the model

```{r}
tic("Training: ")

f <- lda(X_train,Y_train)

toc(log = TRUE)
```
This takes some time...

What's in f ?

```{r}
#f
```


Let's do the inference on the test set now.

```{r}
# Do the inference on the test set
tic("Inference: ")
predictions = predict(f,X_test)
toc(log = TRUE)
Y_pred = as.data.frame(predictions)
Y_pred
```


What does the confusion matrix gives us?

```{r}
writeLines("\n")
mat = confusionMatrix(Y_test, as.factor(Y_pred$class))
mat
```

```{r}
print("END: all the notebook ran.")
Sys.time()

writeLines(paste0("File: ", fileName))
writeLines(paste0("Accuracy: ", mat$overall[1]))
writeLines(paste0(tic.log(format = TRUE)[1][1]))
writeLines(paste0(tic.log(format = TRUE)[2][1]))
```

## Results

### bow_tfidf__min_words_100_2grams_1000__sampling_balanced__cor_cut_0.3_from_1408_to_1110_rm0.csv

Accuracy: 0.735107618111994
Training: : 0.1 sec elapsed
Inference: : 0.11 sec elapsed

Reference
Prediction    0    1
         0 3719 1847
         1 1119 4512
         
### bow_tfidf__min_words_100_2grams_1000__sampling_balanced__cor_cut_0.3_from_1408_to_1110.csv

Accuracy: 0.725739848589126
Training: : 179.6 sec elapsed
Inference: : 6.01 sec elapsed

Reference
Prediction    0    1
         0 3708 2075
         1 1113 4728
         
         
### bow_tfidf__min_words_100_2grams_1000__sampling_balanced__cor_cut_0.5_from_1408_to_1247_rm0.csv

Accuracy: 0.734036012296882
Training: : 179.6 sec elapsed
Inference: : 6.01 sec elapsed

Reference
Prediction    0    1
         0 3714 1916
         1 1112 4643