---
title: "KNN"
output: html_notebook
---

We will compare some classifiers on the "Toxic" column.

Load libraries

```{r}
library(tidyverse)
library(tictoc)
library(caret)
library(class)
source("./parameters.R")
```

# Set the value of K for the run

```{r}
# Number of nearest neighbors taken into account
k = 5
```


# Open the Bag of Word with labels

```{r}
# We open a relatively small Bag of Words in order to limit calculation time
fileName = "bow_tfidf__min_words_100_2grams_1000__sampling_balanced__cor_cut_0.3_from_1408_to_1110_rm0.csv"
df = read_csv(fileName, col_types=col_types_df)
df = df[,-c(2,3,5:9)]
df
```
# Remove lines full of zeros

KNN is not really friend with lines full of zeros in the bag of words.
All these lines have way to many neighbors.
So let's ensure there is none.

```{r}
# Go through each row, return TRUE is at least one value is not zero
non_zero_rows = apply(df[,-1], 1, function(row) any(row !=0 ))
writeLines(paste0("Rows full of zeros: ",sum(!non_zero_rows, na.rm = TRUE)))
# Subset
df = df[non_zero_rows,]
writeLines(paste0("Remaning rows: ",dim(df)[1]))
```


# Splitting the data

```{r}
# Split between train and test
df_train = df[df[1] == 1,-1]
df_test  = df[df[1] == 2,-1]

# Split the test set between features and labels
X_train = df_train[,-1]
Y_train = df_train$df_toxic

# Split the train set between features and labels
X_test = df_test[,-1]
Y_test = df_test$df_toxic
```

# Have a look

```{r}
X_train
as.data.frame(Y_train) 
X_test
as.data.frame(Y_test)
```


# Train the model

```{r}
tic("Training: ")

f <- knn(X_train, X_test, Y_train, k = k)

toc(log = TRUE)
```
This takes some time...

What's in f ?

```{r}
f
```


What does the confusion matrix gives us?

```{r}
writeLines("\n")
mat = confusionMatrix(Y_test, as.factor(f))
mat
```

```{r}
print("END: all the notebook ran.")
Sys.time()

writeLines(paste0("File: ", fileName))
writeLines(paste0("Parameter k: ", k))
writeLines(paste0("Accuracy: ", mat$overall[1]))
writeLines(paste0(tic.log(format = TRUE)[1][1]))
writeLines(paste0(tic.log(format = TRUE)[2][1]))
```

## Results

### bow_tfidf__min_words_100_2grams_1000__sampling_balanced__cor_cut_0.001_from_1408_to_32.csv



