---
title: "SVM"
output: html_notebook
---

We will compare some classifiers on the "Toxic" column.

Load libraries

```{r}
library(tidyverse)
library(tictoc)
library(caret)
source("./parameters.R")
```


# Open the Bag of Word with labels

```{r}
# We open a relatively small Bag of Words in order to limit calculation time
fileName = "bow_tfidf__min_words_100_2grams_1000__sampling_balanced__cor_cut_0.001_from_1408_to_32.csv"
df = read_csv(fileName, col_types=col_types_df)
df = df[,-c(2,3,5:9)]
df
```


# Splitting the data

```{r}
# Split between train and test
df_train = df[df[1] == 1,-1]
df_test  = df[df[1] == 2,-1]

# Split the test set between features and labels
X_train = df_train[,-1]
Y_train = as.factor(df_train$df_toxic)

# Split the train set between features and labels
X_test = df_test[,-1]
Y_test = as.factor(df_test$df_toxic)
```

# Have a look

```{r}
X_train
as.data.frame(Y_train) 
X_test
as.data.frame(Y_test)
```


# Train the model

```{r}
tic("Training: ")

f = svm(X_train,Y_train,kernel = 'linear')
#f = svm(Xl,Yl,kernel = 'radial',gamma = 0.1)

toc(log = TRUE)
```
This takes some time...

What's in f ?

```{r}
f
```


Let's do the inference on the test set now.

```{r}
# Do the inference on the test set
tic("Inference: ")
labels = predict(f,X_test)
toc(log = TRUE)
Y_pred = as.data.frame(labels)
Y_pred
```


What does the confusion matrix gives us?

```{r}
writeLines("\n")
mat = confusionMatrix(Y_test, Y_pred$labels)
mat
```

```{r}
print("END: all the notebook ran.")
Sys.time()

writeLines(paste0("File: ", fileName))
writeLines(paste0("Accuracy: ", mat$overall[1]))
writeLines(paste0(tic.log(format = TRUE)[1][1]))
writeLines(paste0(tic.log(format = TRUE)[2][1]))
```

## Results

### bow_tfidf__min_words_100_2grams_1000__sampling_balanced__cor_cut_0.001_from_1408_to_32.csv

Kernel: linear
Accuracy: 0.569683413626979
Training: : 208.52 sec elapsed
Inference: : 27.52 sec elapsed

